Detecting Facial Expressions in Professional Tennis Matches

### 2017-09-01 Report06-12.Rmd
acknowledgements progress

Google: @Google

@@

Skybiometry: @Skybiometry

@@

ManualClassifiedFaces.csv resulted from the use of the Manual Classification Program, it has information about each face identified manually.
ManualClassifiedScenes.csv also resulted from the use of the app, it contains information about each image.

## Packages
The R package ggplot2 [@ggplot2] was used to make the plots.

>>>>

Google: @Google Refers to the Google Cloud Vision API

@@

Skybiometry: @Skybiometry References the spin off detection and recognition software of Neurotechnology.

@@

ManualClassifiedFaces.csv resulted from the use of the Manual Annotation Application, it contains information about each face identified manually.
ManualClassifiedScenes.csv also resulted from the use of the app, it contains information about each image.

Each script that was automated for POST requests created a classified faces csv.

## Packages
The R packages were used to create the following:

* bookdown [@bookdown] and knitr [@knitr] created the pdf output
* ggplot2 [@ggplot2] was used to make the plots 
* pander [@pander] printed tables
* knitcitations [@knitcitations] and RefManager [@RefManager] allowed for references to be integrated

bookdown
knitr
RefManageR
readr
grid
tidyverse
kfigr
UpSetR
descr
xtable
gtable
ggthemes
EBImage
gridExtra
ggmosaic
